---
title: "S2 Appendix"
author: ""
output: html_document
header-includes:
- \usepackage{multirow}
knit: (function(inputFile, encoding) {
    rmarkdown::render(inputFile, encoding = encoding, output_dir = "../paper/2_final_submission")
  })
---

```{r, echo=FALSE, warning=FALSE, results='hide', message=FALSE}
library(rmarkdown)
library(tidyverse)
library(plotly)
library(rnaturalearth)
library(rnaturalearthdata)
library(gridExtra)
library(cowplot)
library(rprojroot)

path <- find_rstudio_root_file()
```

# Pareto exponents

The below maps plot the Pareto exponents corrected as per Gabaix and Ibragimov (2011) for all the countries included in our data 
set for the years 2000, 2005, 2010 and 2010. The quantiles of the yearly exponent 
distribution are used for the maps with the first quantile always representing 
the countries with the of the smallest Pareto exponent.

```{r, echo=FALSE, warning=FALSE, fig.width = 8}

# load data
path.data <- paste0(path, "/data/data_inter/UN.RData")
load(path.data)

# a zipf table for the appendix, which includes the Zipf coef. per year and country
zipf.table <- net.model$model %>%
  dplyr::select(`as.factor(country)`, `as.factor(year)`, b) %>%
  spread(`as.factor(year)`, b) %>%
  rename(`Countries` = `as.factor(country)`)

# a world `sf` to join with Zipf
world <- ne_countries(scale = "medium", returnclass = "sf")
world <- merge(world, zipf.table, by.x = 'iso_a3', by.y = 'Countries', all = T)

# yearly maps
map2000 <- world %>%
  mutate(eq.n2000 = cut_number(`2000`, 
                               n = 4,
                               labels = c("1st quantile", "2nd quantile",
                                          "3rd quantile", "4th quantile"))) %>%
  ggplot() +
  geom_sf(aes(fill = eq.n2000)) + 
  ggtitle("2000") +
  theme_minimal() + 
  theme(legend.position = "top",
        legend.title = element_blank(),
        plot.title = element_text(hjust = 0.5))

legend <- get_legend(map2000)
map2000 <- map2000 + theme(legend.position="none")


map2005 <- world %>%
  mutate(eq.n2005 = cut_number(`2005`, 
                               n = 4,
                               labels = c("1st quantile", "2nd quantile",
                                          "3rd quantile", "4th quantile"))) %>%
  ggplot() +
  geom_sf(aes(fill = eq.n2005), show.legend = F) + 
  ggtitle("2005") +
  theme_minimal() + 
  theme(legend.title = element_blank(),
        plot.title = element_text(hjust = 0.5))

map2010 <- world %>%
  mutate(eq.n2010 = cut_number(`2010`, 
                               n = 4,
                               labels = c("1st quantile", "2nd quantile",
                                          "3rd quantile", "4th quantile"))) %>%
  ggplot() +
  geom_sf(aes(fill = eq.n2010), show.legend = F) + 
  ggtitle("2010") +
  theme_minimal() +
  theme(legend.title = element_blank(),
        plot.title = element_text(hjust = 0.5))

map2015 <- world %>%
  mutate(eq.n2015 = cut_number(`2015`, 
                               n = 4,
                               labels = c("1st quantile", "2nd quantile",
                                          "3rd quantile", "4th quantile"))) %>%
  ggplot() +
  geom_sf(aes(fill = eq.n2015), show.legend = F) + 
  ggtitle("2015") +
  theme_minimal() +
  theme(legend.title = element_blank(),
        plot.title = element_text(hjust = 0.5))
  

lay <- rbind(c(1,2),
             c(3,4),
             c(5,5))
grid.arrange(map2000, map2005, map2010, map2015, legend,
            nrow=3, 
            heights=c(2.3, 2.3, 0.3),
            layout_matrix = lay)
```

The Pareto exponents are plotted below as an interactive line graph.

```{r, echo=FALSE, warning=FALSE, fig.width = 8}

zipf.line <- zipf.table %>% 
  pivot_longer(!Countries, names_to = "year", values_to = "zipf") %>% 
  ggplot(aes(x=year, y=zipf, group = Countries, colour = Countries),
         show.legend = F) + 
  geom_line() + guides(colour=FALSE) + xlab("Year") +
  ylab("Pareto exponent")  

ggplotly(zipf.line,
         show.legend=F)
  
```